Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2021-10-01 doc/main_jfm.tex
final updates by Rolf

\begin{abstract}
  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic 
  Janus particles suspended in a viscous background flow. 
  The Janus particles interact with each other directly through a hydrophobic attraction potential (HAP)
  that has been shown to model lipid bilayer membranes. In addition they also interact with each other indirectly through the hydrodynamic interactions.
  We adopt an efficient integral equation method for solving the screened
  Laplace equation (for the HAP) and the mobility of Janus particles in a viscous fluid. 
  Both the hydrophobic and hydrodynamic interactions between near
  touched boundaries are accurately captured within the integral formulation. Under a linear shear flow,  we observe the tank-treading deformation
  in a two-dimensional vesicle made of Janus particles for various values of the shear rate.
  The results yield measurements 
  of inter-monolayer friction and membrane permeability. Large shear rates lead to membrane rupture. 
  The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
  interactions in shear and extensional flows. We find that the hydrodynamics of a  vesicle assembled from Janus particles
replicates the dynamics of an inextensible elastic vesicle.
%    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
%  In this work, we study the dynamics of many-body systems immersed in a
%  viscous fluid with a specified interparticle force. In particular, we
%  apply a hydrophobic attraction potential (HAP) using a Janus type
%  granular system to model lipid bilayer membranes. Coupling with an
%  efficient integral equation method for rigid bodies in Stokes flow and
%  a previous developed HAP solver, the deformations of a two-dimensional
%  vesicle such as tank-treading motion and membrane ruptures can be
%  observed under different values of the shear rate. Moreover, an
%  efficient integral equation method is adopted for solving the screened
%  Laplace equation and the mobility problem where it can accurately
%  calculate hydrophobic and hydrodynamic interactions between near
%  touched boundaries.
\end{abstract}

@@

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective of this work is to study the hydrodynamics of JP vesicles
in background flows. We consider an $N_b$-many body collection of JP
suspended in a two-dimensional unbounded domain $\Omega$. The boundary
of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
Since each particle $\Gamma_i$ with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
\label{eq:rigid_bc}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force and torque
balance gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu_i$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we use the velocity
representation of~\cite{pow-mir1987}. In particular, we write the
velocity as the sum of a double-layer potential and $N_b$-many Stokeslets and
rotlets
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{|\rr|^2} \frac{\rr \otimes \rr}{|\rr|^2}
    \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and rotlets
centered at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
    \frac{\rr \otimes \rr}{|\rr|^2}\right) \FF_i, \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
\end{align}
respectively, where $\rr = \xx - \aa_i$. The
Stokeslet is torque-free and has force $\FF_i$ while the rotlet is
force-free and has torque $T_i$. Therefore, the
velocity~\eqref{eq:velocity} satisfies the total force~\eqref{eq:force}
and torque~\eqref{eq:torque} conditions if the double-layer potential
$\DD[\eeta]$ is force- and torque-free.  Matching the limit
of~\eqref{eq:velocity} with the rigid body motion, and imposing that
$\DD[\eeta]$ is force- and torque-free, the density function $\eeta$,
translational velocity $\vv_i$, and angular velocity $\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu_i \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

@@

\subsection{Model Parameters}
\cite{Fu20} studied physical quantities for static JP vesicles for
various particle shapes. In the present study, we fix the particle shape
and vary the background flows. Specifically, the particles are circular
disks with diameter $l_0 = 2.5$~nm. The boundary
conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
\theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle center
and director respectively. The particle diameter is the thickness of
monolayers and the director points in the direction of the hydrophobic
side of the JP.

@@

%\subsection{Jeffery Orbit}
%We use Jeffery orbits to numerically validate our solver for the mobility-problem.  
%The background flow is a shear flow $\uu_{\infty}(\xx) = \dot\gamma  \xx \cdot \mathbf{e}_2 \mathbf{e}_1$ with shear rate $\dot\gamma$
%and orthogonal unit vectors $\mathbf{e}_1$ and $\mathbf{e}_2$. 
%A single elliptical particle is suspended in the fluid with center at the origin.
%The Jeffrey orbit  
%\begin{equation}
%\label{eq:jeff}
%\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right)
%\end{equation}
%gives the angle between the major axis and $\mathbf{e}_2$
%where $a$, $b$ are the semi-major and semi-minor axes. 
%We are assuming $\Theta(0) = 0$.
%Figure~\ref{figure1} shows that the angles coming from the integral equation method \eqref{eq:SKIE}-\eqref{eq:mobility2}
%are in complete agreement with the theoretical time course \eqref{eq:jeff}.  Hydrophobic attraction and repulsion are zero for a single particle. 
%
%
%\begin{figure}
%\centering
%\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
%\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
%  \caption{The figure compares the theoretical Jeffery orbit for $\Theta(t)$ and the result from the integral equation method. 
%    The insets show the simulation setup. The shear rate is $\dot\gamma=0.1$.}
%    \label{figure1}
%\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Inter-Monolayer Friction}
We observe inter-monolayer slip in the tank-treading, JP vesicle at all
shear rates. Since they are not bound, the two leaflets of the vesicle
are able to slide past one another. This sliding is limited by viscous
friction of the aqueous gaps between particles and by the constant
unbinding and binding of particles pairs in apposing leaflets. 
Previous studies \cite{Zgorski2019, denOtter2007}
have considered inter-monolayer slip in lipid bilayers simulated by MD.

@@

To calculate $U$, we let $v_+(\mathbf{x})$ and $v_-(\mathbf{x})$ 
be the tangential velocity of the outer, respectively inner, leaflet.  Then 
\begin{equation}
U = \frac{1}{L}\int_{C_M}v_+(\mathbf{x})(1 - \delta \kappa) - v_-(\mathbf{x})(1 +  \delta \kappa) \, ds,
\end{equation}
where $ \delta $ is the distance from the leaflet centers to the midplane and $\kappa$ is the curvature. 
The factors $\pm  \delta \kappa$ are needed to project the leaflet velocities, defined on the particle centers,
onto the midplane curve. 
Finally, the function $s(t) = \int_0^t dU $ records the distance one leaflet has
slid past the other. Figure~\ref{figure5}b plots the sliding distance for various shear
rates.

Table~\ref{table1} provides dimensional friction coefficients $b$ for
several shear rates. 
The coefficients are 0.79 $\pm$ 0.3 pN ns nm$^{-3}$ which is in good quantitative agreement with values
previously reported in the literature (\cite{sch-vla-mik2010}
and~\cite{denOtter2007}). \cite{denOtter2007} give $b = 2.4 \times 10^6$
Pa m$^{-1}$ s = 2.4 pN ns nm$^{-3}$  from their MD study, for example.

\subsubsection{Membrane Ruptures}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Tank-treading leads to membrane rupture for
  large shear rates.} 
\end{figure}
A temporary fissure or a complete membrane rupture can occur at large
shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
when suspended in a shear flow. For $\chi = 0.1$, starting with a
circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
background flow and fissures appear in the bilayer structure in multiple
locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
ruptured vesicles form two planar micelles which are eventually carried
off by the flow (Figure~\ref{figure8}d).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
Finally, we consider the parabolic background flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( 
    \frac{\xx \cdot \mathbf{e}_y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ determines the shape of the
flow. The parameter $R_0$ is the radius of the JP vesicle at $t=0$ and
$w$ sets the width of the profile. \cite{Kaoui09, cou-kao-pod-mis2008,
dan-vla-mis2009} have shown that the behavior of a vesicle in this
unbounded flow includes vertical migration, and depending on the flow
rate and reduced area, the steady-state shape can be either a symmetric
parachute or an asymmetric slipper.

@@

Figure~\ref{figure2}c plots the data for the pressure jump $\Delta p$
between the particle center and the far-field (see
Figures~\ref{figure2}c and~\ref{figure2}d). We use $R = L/(2\pi)$ for
the vesicle radius, and the horizontal axis is the relative stretch.
The circles are data for a vesicle with radius 17 nm. The linear fit
(solid lines) shows that $R\Delta P$ is proportional to the relative
stretching $L/L_0 - 1$. The squares are for a vesicle with twice the
radius 34 nm, and the data overlap supports that the proportionality
constant $K_A$ is a stretching modulus that is independent of vesicle
size. The data give $K_A = 170 \pm 9$ pN nm$^{-1}$ which is in good
agreement with the experimentally obtained area moduli of lipid bilayer. 
To evaluate how changes to particle size lead to different
physical properties, the asterisk symbols are for an 18 nm radius
vesicle consisting of particles with diameter 1.25 nm, instead of the
usual 2.5 nm. These data give a smaller stretching modulus of $K_A =
102$~pN~nm$^{-1}$.

@@

We show snapshots of the fluid pressure in Figure~\ref{figure10}. Since the
initial JP vesicles are pre-relaxed, there is initially no pressure jump
between the internal and external fluids (panel (a)). Panels (b)--(d)
show the configurations when $t = \{0.5,1,1.5\}$ $\upmu$s, and the
streamlines are plotted in the background for all panels. 
We include the numerical results from a continuum model in all insets and these
comparisons give a qualitative agreement between two models.
We also observe an adhesive
effect between the two JP vesicles that is set up by the hydrophobic
attraction (Figure~\ref{figure10}c). Similar dynamics have been observed between a pair of adhering vesicles in a shear flow
(\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
behavior is absent when two JP vesicles are well-separated.

@@

Figure~\ref{figure12} shows numerical results when the centroids of the
two Janus particles are placed at $(-10,-0.1)$~nm and $(10,0.1)$~nm
(case (iii) from Figure~\ref{figure11}). With this setup, the two JP
vesicles eventually separate along the $\pm y$-directions and we compare
the results against a continuum model as shown in all insets. Panels
(b)--(d) show the transient behavior of the JP vesicles and the
continuum vesicles under an extensional flow. In both the coarse-grained
model and the continuum model, the vesicles initially converge towards
one other and then diverge along the $y$-axis. The behavior of the
streamlines in both cases are similar. The pressure is initially largest
in the gap formed by two JP vesicles and decreases during the
separation. The short-range repulsion plays an important role to avoid
particle collisions.
%and this result can be
%compared with some findings in continuum modeling simulations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{conclusion}Conclusion}

@@

We also simulate the spatial migration of a JP vesicle in a parabolic
shear flow. 
%The chosen parameter values result in an asymmetric
%slipper shape. 
%
Replicating the hydrodynamics of a GUV in a Poiseuille
flow~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}), the JP
vesicle moves toward the center of the shear flow. While the initial
reduced area of the JP vesicle is $A^* \approx 1$, the equilibrium
reduced area is $A^*=0.9$. For the parameters we used in the simulation,
the JP vesicle takes on an asymmetric, ``slipper" shape as it settles
above the center of flow and exhibits tank-treading motion.
%A qualitative
%agreement is made by comparing the JP vesicle shape with the
%two-dimensional inextensible membrane in continuum modeling
%simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). 
An interesting result contrast with continuum results is that the JP
vesicle oscillates at a height slightly above the center of the
Poiseuille flow.

>>>>

\begin{abstract}
  We develop a new model, to our knowledge,  for the many-body  hydrodynamics of amphiphilic 
  Janus particles suspended in a viscous background flow. 
  The Janus particles interact through a hydrophobic attraction potential 
  that leads to self-assembly into bilayer structures.   
  We adopt an efficient integral equation method for solving the screened
  Laplace equation for hydrophobic attraction and 
  for solving the mobility problem for hydrodynamic interactions. 
  The integral equation formulation accurately captures both interactions for near touched boundaries. 
  Under a linear shear flow,  we observe the tank-treading deformation
  in a two-dimensional vesicle made of Janus particles.
  The results yield measurements of inter-monolayer friction, membrane permeability, 
  and at large shear rates, membrane rupture. 
  The simulations studies include a vesicle in parabolic flow and vesicle-vesicle 
  interactions in shear and extensional flows. The hydrodynamics of the Janus 
  particles vesicle replicate the behaviour of an inextensible elastic vesicle membrane.
%    We develop a new model, to our knowledge,  for the hydrodynamics of amphiphilic particles in background flows. 
%  In this work, we study the dynamics of many-body systems immersed in a
%  viscous fluid with a specified interparticle force. In particular, we
%  apply a hydrophobic attraction potential (HAP) using a Janus type
%  granular system to model lipid bilayer membranes. Coupling with an
%  efficient integral equation method for rigid bodies in Stokes flow and
%  a previous developed HAP solver, the deformations of a two-dimensional
%  vesicle such as tank-treading motion and membrane ruptures can be
%  observed under different values of the shear rate. Moreover, an
%  efficient integral equation method is adopted for solving the screened
%  Laplace equation and the mobility problem where it can accurately
%  calculate hydrophobic and hydrodynamic interactions between near
%  touched boundaries.
\end{abstract}

@@

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective of this work is to study the hydrodynamics of JP vesicles
in background flows. We consider an $N_b$-many body collection of JP
suspended in a two-dimensional unbounded domain $\Omega$. The boundary
of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
\label{eq:rigid_bc}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force and torque
balance gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu_i$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we use the velocity
representation of~\cite{pow-mir1987}. In particular, we write the
velocity as the sum of a double-layer potential and $N_b$-many Stokeslets and
rotlets
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{|\rr|^2} \frac{\rr \otimes \rr}{|\rr|^2}
    \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$ and $\rho = |\rr|$. The Stokeslet and rotlets
centred at $\aa_i$ are
\begin{align}
  \SS(\xx,\aa_i)\FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
    \frac{\rr \otimes \rr}{|\rr|^2}\right) \FF_i, \\
  \RR(\xx,\aa_i)T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
\end{align}
respectively, where $\rr = \xx - \aa_i$. The
Stokeslet is torque-free and has force $\FF_i$ while the rotlet is
force-free and has torque $T_i$. Therefore, the
velocity~\eqref{eq:velocity} satisfies the total force~\eqref{eq:force}
and torque~\eqref{eq:torque} conditions if the double-layer potential
$\DD[\eeta]$ is force- and torque-free.  Matching the limit
of~\eqref{eq:velocity} with the rigid body motion, and imposing that
$\DD[\eeta]$ is force- and torque-free, the density function $\eeta$,
translational velocity $\vv_i$, and angular velocity $\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\bd\Gamma_i} \eeta \cdot \nnu_i \, \dif s &= {\bf 0}, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\bd\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu_i \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

@@

\subsection{Model Parameters}
\cite{Fu20} studied physical quantities for static JP vesicles for
various particle shapes. In the present study, we fix the particle shape
and vary the background flows. Specifically, the particles are circular
disks with diameter $l_0 = 2.5$~nm. The boundary
conditions~\eqref{eq:SLbc} are $f_i(\xx) = \tfrac{1}{2}(1 + \cos
\theta_i)$ where $\theta_i$ is the angle between $\xx - \aa_i$ and
$\dd_i$, where the vectors $\aa_i$ and $\dd_i$ are the particle centre
and director respectively. The particle diameter is the thickness of
monolayers and the director points in the direction of the hydrophobic
side of the JP.

@@

%\subsection{Jeffery Orbit}
%We use Jeffery orbits to numerically validate our solver for the mobility-problem.  
%The background flow is a shear flow $\uu_{\infty}(\xx) = \dot\gamma  \xx \cdot \mathbf{e}_2 \mathbf{e}_1$ with shear rate $\dot\gamma$
%and orthogonal unit vectors $\mathbf{e}_1$ and $\mathbf{e}_2$. 
%A single elliptical particle is suspended in the fluid with centre at the origin.
%The Jeffrey orbit  
%\begin{equation}
%\label{eq:jeff}
%\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right)
%\end{equation}
%gives the angle between the major axis and $\mathbf{e}_2$
%where $a$, $b$ are the semi-major and semi-minor axes. 
%We are assuming $\Theta(0) = 0$.
%Figure~\ref{figure1} shows that the angles coming from the integral equation method \eqref{eq:SKIE}-\eqref{eq:mobility2}
%are in complete agreement with the theoretical time course \eqref{eq:jeff}.  Hydrophobic attraction and repulsion are zero for a single particle. 
%
%
%\begin{figure}
%\centering
%\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
%\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
%  \caption{The figure compares the theoretical Jeffery orbit for $\Theta(t)$ and the result from the integral equation method. 
%    The insets show the simulation setup. The shear rate is $\dot\gamma=0.1$.}
%    \label{figure1}
%\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Inter-Monolayer Friction}
We observe inter-monolayer slip in the tank-treading, JP vesicle at all
shear rates. Since they are not bound, the two leaflets of the vesicle
are able to slide past one another. 
Monolayer slip effects have been incorporated in continuum models (\cite{sch-vla-mik2010}).
In the present setting, slip is limited by viscous
friction of the aqueous gaps between particles and by the constant
unbinding and binding of particles pairs in apposing leaflets.

@@

To calculate $U$, we let $u_+(\mathbf{x})$ and $u_-(\mathbf{x})$ 
be the tangential velocity of the outer, respectively inner, leaflet.  Then 
\begin{equation}
U = \frac{1}{L}\int_{C_M}u_+(\mathbf{x})(1 - \delta \kappa) - v_-(\mathbf{x})(1 +  \delta \kappa) \, ds,
\end{equation}
where $ \delta $ is the distance from the leaflet centres to the midplane and $\kappa$ is the curvature. 
The factors $\pm  \delta \kappa$ are needed to project the leaflet velocities, defined on the particle centres,
onto the midplane curve. 
Finally, the function $s(t) = \int_0^t dU $ records the distance one leaflet has
slid past the other. Figure~\ref{figure5}b plots the sliding distance for various shear
rates.

Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
over a range of shear rates
which is in good quantitative agreement with values previously reported in the literature.
Atomistic studies have also considered inter-monolayer slip in lipid bilayers. 
\cite{WuoEd06} and \cite{denOtter2007} reported $b = 0.7 \times 10^6$ Pa m$^{-1}$ s  
$=0.7$ pN ns nm$^{-3}$  
and $b = 2.4$  pN ns nm$^{-3}$ for DPPC membranes simulated by MD, respectively. 
Using a more recent version of the Martini force field, \cite{Zgorski2019} 
gives $b = 5.5$ pN ns nm$^{-3}$ for shear rates 0.4 ns$^{-1}$ and higher.
It is understandable that there is uncertainty in the friction coefficients of
Table~\ref{table1}.  The scatter in our data, however, is fully consistent with that calculated
from MD simulations, c.f. the transient rise in values of Table~\ref{table1} and in \cite{Zgorski2019}, Figure 10
for low shear rates. 
\subsubsection{Membrane Ruptures}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Tank-treading leads to membrane rupture for
  large shear rates.} 
\end{figure}
A temporary fissure or a complete membrane rupture can occur at large
shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
when suspended in a shear flow. For $\chi = 0.1$, starting with a
circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
background flow and fissures appear in the bilayer structure in multiple
locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
ruptured vesicles form two planar micelles which are eventually carried
off by the flow (Figure~\ref{figure8}d).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
Finally, we consider the parabolic background flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( 
    \frac{\xx \cdot \mathbf{e}_y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ determines the shape of the
flow. The parameter $R_0$ is the radius of the JP vesicle at $t=0$ and
$w$ sets the width of the profile. \cite{Kaoui09, cou-kao-pod-mis2008,
dan-vla-mis2009} have shown that the behaviour of a vesicle in this
unbounded flow includes vertical migration, and depending on the flow
rate and reduced area, the steady-state shape can be either a symmetric
parachute or an asymmetric slipper.

@@

Figure~\ref{figure2}c plots the data for the pressure jump $\Delta p$
between the particle centre and the far-field (see
Figures~\ref{figure2}c and~\ref{figure2}d). We use $R = L/(2\pi)$ for
the vesicle radius, and the horizontal axis is the relative stretch.
The circles are data for a vesicle with radius 17 nm. The linear fit
(solid lines) shows that $R\Delta P$ is proportional to the relative
stretching $L/L_0 - 1$. The squares are for a vesicle with twice the
radius 34 nm, and the data overlap supports that the proportionality
constant $K_A$ is a stretching modulus that is independent of vesicle
size. The data give $K_A = 170 \pm 9$ pN nm$^{-1}$ which is in good
agreement with the experimentally obtained area moduli of lipid bilayer. 
To evaluate how changes to particle size lead to different
physical properties, the asterisk symbols are for an 18 nm radius
vesicle consisting of particles with diameter 1.25 nm, instead of the
usual 2.5 nm. These data give a smaller stretching modulus of $K_A =
102$~pN~nm$^{-1}$.

@@

We show snapshots of the fluid pressure in Figure~\ref{figure10}. Since the
initial JP vesicles are pre-relaxed, there is initially no pressure jump
between the internal and external fluids (panel (a)). Panels (b)--(d)
show the configurations when $t = \{0.5,1,1.5\}$ $\upmu$s, and the
streamlines are plotted in the background for all panels. 
We include the numerical results from a continuum model in all insets and these
comparisons give a qualitative agreement between two models.
We also observe an adhesive
effect between the two JP vesicles that is set up by the hydrophobic
attraction (Figure~\ref{figure10}c). Similar dynamics have been observed between a pair of adhering vesicles in a shear flow
(\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
behaviour is absent when two JP vesicles are well-separated.

@@

Figure~\ref{figure12} shows numerical results when the centroids of the
two Janus particles are placed at $(-10,-0.1)$~nm and $(10,0.1)$~nm
(case (iii) from Figure~\ref{figure11}). With this setup, the two JP
vesicles eventually separate along the $\pm y$-directions and we compare
the results against a continuum model as shown in all insets. Panels
(b)--(d) show the transient behaviour of the JP vesicles and the
continuum vesicles under an extensional flow. In both the coarse-grained
model and the continuum model, the vesicles initially converge towards
one other and then diverge along the $y$-axis. The behaviour of the
streamlines in both cases are similar. The pressure is initially largest
in the gap formed by two JP vesicles and decreases during the
separation. The short-range repulsion plays an important role to avoid
particle collisions.
%and this result can be
%compared with some findings in continuum modeling simulations.

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{conclusion}Conclusion}

@@

We also simulate the spatial migration of a JP vesicle in a parabolic
shear flow. 
%The chosen parameter values result in an asymmetric
%slipper shape. 
%
Replicating the hydrodynamics of a GUV in a Poiseuille
flow~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}), the JP
vesicle moves toward the centre of the shear flow. While the initial
reduced area of the JP vesicle is $A^* \approx 1$, the equilibrium
reduced area is $A^*=0.9$. For the parameters we used in the simulation,
the JP vesicle takes on an asymmetric, ``slipper" shape as it settles
above the centre of flow and exhibits tank-treading motion.
%A qualitative
%agreement is made by comparing the JP vesicle shape with the
%two-dimensional inextensible membrane in continuum modeling
%simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). 
An interesting result contrast with continuum results is that the JP
vesicle oscillates at a height slightly above the centre of the
Poiseuille flow.
